Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-18 Manuscript/manuscript.tex
MS update: added volmap figures with a small commentary paragraph.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities2.eps}
  \caption{\label{fig:cacl-dens}
    Number density of \ce{Ca^{2+}} and \ce{Cl^-} as a function of membrane normal axis
    for different force fields. Data for Lipid14 with \AA{}qvist ions are taken directly from Ref. \citenum{catte16}
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    Densities of~\ce{Cl^-}) and water are divided with 2 and 200, respectively, to visalize them
    with the same scale as \ce{Ca^{2+}}. The molar concentration in water is 350~mM in all systems
    presented here. 
    }
  \todo{PAVEL: draw phosphate position with its variance, add water density (scaled) and include the number of$\Gamma$-surface access.} \\
  \todo{JOE: Change the figure so that it contains a membrane background} \\
  \todo{Resuls with Lipid14+Dang to be added once done.}
\end{figure}

@@

@@

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities2.eps}
  \caption{\label{fig:cacl-dens}
    Number density of \ce{Ca^{2+}} and \ce{Cl^-} as a function of membrane normal axis
    for different force fields. Data for Lipid14 with \AA{}qvist ions are taken directly from Ref. \citenum{catte16}.
    Relative surface excess for the respective simulations are: 
    Lipid14 with \AA{}qvist ions $\Gamma_i^w = XX nm^{-3}$; 
    Lipid14 with Dang ions $\Gamma_i^w = 0.3 nm^{-3}$; 
    ECC-lipids with ECC-ions $\Gamma_i^w = 0.07 nm^{-3}$. 
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    Densities of~\ce{Cl^-} and water are divided with 2 and 200, respectively, to visalize them
    with the same scale as \ce{Ca^{2+}}. The molar concentration of the ions in water is 350~mM in all systems
    presented here. 
    }
  \todo{Calculate the surface excess for L14+Aqvist sim.}
  \todo{PAVEL: draw phosphate position with its variance, add water density (scaled) and include the number of$\Gamma$-surface access.} \\
  \todo{JOE: Change the figure so that it contains a membrane background} \\
  \todo{Resuls with Lipid14+Dang to be added once done -- running with larger box.}
\end{figure}

@@

In addition, we estimated the relative binding affinities of several moieties in POPC:
phosphate moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
Using the probability isodensity contours (see Fig.~\ref{fig:volmaps}), 
we estimate that the largest contribution
to the binding of \ce{Ca2+} to POPC membranes likely comes from the phosphate group. 
Although the isodensity plots are relatively easy to interpret,
the contours shown in Fig.~\ref{fig:volmaps} cannot conclusively tell on the details
of \ce{Ca2+} binding to any of the two carbonyl moieties.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} \\
  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Contours of probability isodensities of \ce{Ca2+} with respect to 
      various moieties fixed in space (highlighted with transparent spheres): 
      phosphate moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      Shown contours suggest that the dominant contribution 
      to \ce{Ca2+} binding likely comes from the phosphate group, 
      but remain inconclusive on the details of the interactions with any of the two carbonyl groups. 
  }
\end{figure}
